Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-05 ch04-lrmhinf/ch04appendices.inc.tex
Add photo details of AVIS
Fix some captions

\begin{figure}
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-setup.pdf}
  \caption{Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
  \label{fig:avis:simulink:setup}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners. For each of the actuators and sensors, the color indicates the principal direction.}
  \label{fig:avis:withAxes}
\end{figure}

@@

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function matrix that is implemented as a discrete state-space model.
This controller was constructed by~\citet{Rademakers2005MSc}
 and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef 
  \begin{cases}
     x[n+1] &= A x[n] + B u_c\\
       y_c    &= C x + D u_c 
  \end{cases}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are common among the translational directions and the rotational directions respectively, such that
\begin{equation}
  \experimental\Controller = 
  \AvisMatrixDiagonal{\experimental\Controller_{\mathrm{tran}}}{\experimental\Controller_{\mathrm{rot}}}
\end{equation}
with
\begin{align}
\experimental\Controller_{\mathrm{tran}} &  \approx 
   \frac{4.9821 z + 4.6787}{ z - 0.8282} \cdot 10^{-3} \\
  \experimental\Controller_{\mathrm{rot}} & \approx 
    \frac{0.88595 z + 0.83201}{ z - 0.8282} \cdot 10^{-3}
\end{align}
 as visualized in \figref{fig:avis:bodeplots:controllerAndSensor}.

\begin{figure}[p]
\setlength\figurewidth{0.75\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/avis-setup-filters.tikz}
\caption{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
\label{fig:avis:bodeplots:controllerAndSensor}
\end{figure}

@@

\begin{figure}[p]
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
  \caption{Simulink model of the AVIS sub-block.}
  \label{fig:avis:simulink:avis}
\end{figure}

>>>>

\begin{figure}
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-setup.pdf}
  \caption[\Simulink model used on the \glsentrytext{AVIS}]{\Simulink model used during the AVIS measurements. All signals are six-dimensional real values.}
  \label{fig:avis:simulink:setup}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption[\glsentrytext{AVIS} with coordinate frame, sensors and actuators.]{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners. For each of the actuators and sensors, the color indicates the principal direction.}
  \label{fig:avis:withAxes}
\end{figure}

@@

Specifically, $\experimental\Controller$ is a $6\times6$ transfer function matrix that is implemented as a discrete state-space model.
This controller was constructed by~\citet{Rademakers2005MSc}
 and is given by the state-space matrices below
\begin{align}
  \experimental\Controller & \isdef 
  \begin{cases}
     x[n+1] &= A x[n] + B u_c[n]\\
       y_c[n]   &= C x[n] + D u_c[n] 
  \end{cases}\\
  A       &\approx 828.8 \cdot 10^{-3} \cdot \Identity{6} \\
  B = C &\approx \AvisMatrixDiagonal{93.83}{39.57} \cdot 10^{-3}\\
  D       &= \AvisMatrixDiagonal{4.982}{0.886} \cdot 10^{-3}
\end{align}
with $\Identity{n}$ the $n\times n$ identify matrix.
It can be seen that the controller is diagonal, i.e. the directions are decoupled, and that the dynamics are common among the translational directions and the rotational directions respectively, such that
\begin{equation}
  \experimental\Controller = 
  \AvisMatrixDiagonal{\experimental\Controller_{\mathrm{tran}}}{\experimental\Controller_{\mathrm{rot}}}
\end{equation}
with
\begin{align}
\experimental\Controller_{\mathrm{tran}} &  \approx 
   \frac{4.9821 z + 4.6787}{ z - 0.8282} \cdot 10^{-3} \\
  \experimental\Controller_{\mathrm{rot}} & \approx 
    \frac{0.88595 z + 0.83201}{ z - 0.8282} \cdot 10^{-3}
\end{align}
 as visualized in \figref{fig:avis:bodeplots:controllerAndSensor}.

\begin{figure}[p]
\setlength\figurewidth{0.75\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/avis-setup-filters.tikz}
\caption[\glsentrytext{AVIS} controller and filters]{Bode plots of the elements of $\experimental\Controller$ and sensor filter $F$ present in the set-up.}
\label{fig:avis:bodeplots:controllerAndSensor}
\end{figure}

@@

\begin{figure}[p]
\setlength\figurewidth{\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/simulink-avis.pdf}
  \caption{\Simulink model of the \glsentrytext{AVIS} sub-block.}
  \label{fig:avis:simulink:avis}
\end{figure}
